Haul-out behavior and aerial survey detectability of seals in the Bering and Chukchi seas

### 2021-04-15 analysis/paper/paper.Rmd
EXPAND FIG CAPS/ADD {ggtext} SUPPORT

  df <- data.frame(
    age_sex = a_s,
    solar_hour = rep(0:23, each = n_days),
    yday = rep(start_day:end_day, times = 24),
    northing = mean(data$northing),
    temp2 = temp_pred,
    wind = wind_pred,
    pressure = baro_pred,
    precip = precip_pred
  ) %>%
    mutate(
      sin1 = sin(pi * solar_hour / 12),
      cos1 = cos(pi * solar_hour / 12),
      sin2 = sin(pi * solar_hour / 6),
      cos2 = cos(pi * solar_hour / 6),
      sin3 = sin(pi * solar_hour / 4),
      cos3 = sin(pi * solar_hour / 4),
    ) %>%
    mutate(day = (yday - 120) / 10,
           day2 = day ^ 2,
           day3 = day ^ 3)
  df_list[[a_s]] <- df
  }
  if(length({{age_sex}}) > 1) {
  df_out <- bind_rows(df_list) %>%
    mutate(age_sex = forcats::fct_relevel(
      age_sex,c("ADULT.F","ADULT.M","SUBADULT","YOUNG-OF-THE YEAR"))
    )
  } else {
    df_out <- bind_rows(df_list)
  }
}
```

@@

```{r ribbonHOwx, fig.height = 5.5, include=TRUE, fig.id = "ribbonHOwx", fig.cap="Variability in predicted haul-out probability of ribbon seals across a range of weather conditions thea range of weather conditions encountered in the observed data. Transparent vertical lines represent the 95% confidence interval around the predicted haul-out probability. Solid lines are smoothed fits to the predictions and provided to better indicate the marginal effect."}

@@

```{r spottedHOwx,fig.height = 5.5, include=TRUE, fig.id = "spottedHOwx", fig.cap="Variability in the predicted haul-out probability of spotted seals across a range of weather conditions thea range of weather conditions encountered in the observed data. Transparent vertical lines represent the 95% confidence interval around the predicted haul-out probability. Solid lines are smoothed fits to the predictions and provided to better indicate the marginal effect."}
library(ggsci)

@@

```{r beardedHOwx,fig.height = 5.5, include=TRUE, fig.id = "beardedHOwx", fig.cap="Variability in predicted haul-out probability of bearded seals across a range of weather conditions thea range of weather conditions encountered in the observed data. Transparent vertical lines represent the 95% confidence interval around the predicted haul-out probability. Solid lines are smoothed fits to the predictions and provided to better indicate the marginal effect."}

@@

```{r maxextentHO, fig.height = 5.5, include=TRUE, fig.id = "maxextent", fig.cap="Annual timing of peak haul-out behavior analyzed against the yearly maximum area of sea ice extent in the study area. While spotted seal adult females and subadults show a negative trend line, none of the relationships were determined to be significant."}
ggplot(data = peak_ho_df, aes(y = yday, x = max_extent_km2, color = species)) + 
  geom_smooth(method = "lm", alpha = 0.2, aes(fill = species)) +
  geom_point() +
  facet_grid(age_sex~.) +
  scale_y_continuous(breaks = c(125,135,145, 156),
                     labels = c("05-May", "15-May", "25-May", "05-Jun")) +
  scale_color_manual(values = c('#E66100','#5D3A9B'), name = "") +
  scale_fill_manual(values = c('#E66100','#5D3A9B'), name = "") +
  theme(legend.position = "top",
        legend.justification = "right") +
  labs(y = "date of peak haul-out", x = "maximum sea ice extent (km^2^ / 1000)",
       title = "The connection between yearly maximum sea ice extent and the \ntiming of peak haul-out probability is limited") +
  theme(axis.text.x = element_markdown())

>>>>

  df <- data.frame(
    age_sex = a_s,
    solar_hour = rep(0:23, each = n_days),
    yday = rep(start_day:end_day, times = 24),
    northing = mean(data$northing),
    temp2 = temp_pred,
    wind = wind_pred,
    pressure = baro_pred,
    precip = precip_pred
  ) %>%
    mutate(
      sin1 = sin(pi * solar_hour / 12),
      cos1 = cos(pi * solar_hour / 12),
      sin2 = sin(pi * solar_hour / 6),
      cos2 = cos(pi * solar_hour / 6),
      sin3 = sin(pi * solar_hour / 4),
      cos3 = sin(pi * solar_hour / 4),
    ) %>%
    mutate(day = (yday - 120) / 10,
           day2 = day ^ 2,
           day3 = day ^ 3)
  df_list[[a_s]] <- df
  }
  if(length({{age_sex}}) > 1) {
  df_out <- bind_rows(df_list) %>%
    mutate(age_sex = forcats::fct_relevel(
      age_sex,c("ADULT.F","ADULT.M","SUBADULT","YOUNG OF YEAR"))
    )
  } else {
    df_out <- bind_rows(df_list)
  }
}
```

@@

```{r ribbonHOwx, fig.height = 5.5, include=TRUE, fig.id = "ribbonHOwx", fig.cap="Variability in predicted haul-out probability of ribbon seals across a range of weather conditions the range of weather conditions encountered in the observed data. Transparent vertical lines represent the 95% confidence interval around the predicted haul-out probability. Solid lines are smoothed fits to the predictions and provided to better indicate the marginal effect."}

@@

```{r spottedHOwx,fig.height = 5.5, include=TRUE, fig.id = "spottedHOwx", fig.cap="Variability in the predicted haul-out probability of spotted seals across a range of weather conditions the range of weather conditions encountered in the observed data. Transparent vertical lines represent the 95% confidence interval around the predicted haul-out probability. Solid lines are smoothed fits to the predictions and provided to better indicate the marginal effect."}
library(ggsci)

@@

```{r beardedHOwx,fig.height = 5.5, include=TRUE, fig.id = "beardedHOwx", fig.cap="Variability in predicted haul-out probability of bearded seals across a range of weather conditions the range of weather conditions encountered in the observed data. Transparent vertical lines represent the 95% confidence interval around the predicted haul-out probability. Solid lines are smoothed fits to the predictions and provided to better indicate the marginal effect."}

@@

```{r maxextentHO, fig.height = 5.5, include=TRUE, fig.id = "maxextent", fig.cap="Annual timing of peak haul-out behavior analyzed against the yearly maximum area of sea ice extent in the study area. While spotted seal adult females and subadults show a negative trend line, none of the relationships were determined to be significant."}
ggplot(data = peak_ho_df, aes(y = yday, x = max_extent_km2, color = species)) + 
  geom_smooth(method = "lm", alpha = 0.2, aes(fill = species)) +
  geom_point() +
  facet_grid(age_sex~.) +
  scale_y_continuous(breaks = c(125,135,145, 156),
                     labels = c("05-May", "15-May", "25-May", "05-Jun")) +
  scale_color_manual(values = c('#E66100','#5D3A9B'), name = "") +
  scale_fill_manual(values = c('#E66100','#5D3A9B'), name = "") +
  theme(legend.position = "top",
        legend.justification = "right") +
  labs(y = "date of peak haul-out", x = "maximum sea ice extent (km<sup>2</sup> / 1000)",
       title = "The connection between yearly maximum sea ice extent and the \ntiming of peak haul-out probability is limited") +
  theme(axis.title.x = element_markdown())
